---
title: "Machine Learning Project"
output: html_document
---


### Loading libraries
```{r}
library(caret)
library(dplyr)
library(randomForest)
```

### Loading the data
We will load the data from the URL. The CSV has been download earlier.

```{r}
setwd("E:\\Dev\\R\\Coursera\\8 Machine\\")
#fileUrldata <-"https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
#download.file(fileUrldata, destfile = "./pml-training.csv") 
data<-read.csv("pml-training.csv")

```


We will only use the variables that don't have NA values
```{r}
dataframevar<-select(data, num_window, roll_belt, pitch_belt, yaw_belt, total_accel_belt, gyros_belt_x, gyros_belt_y, gyros_belt_z, accel_belt_y, accel_belt_x, accel_belt_z, magnet_belt_x, magnet_belt_y, magnet_belt_z, roll_arm, pitch_arm, yaw_arm, total_accel_arm, gyros_arm_x, gyros_arm_y, gyros_arm_z, accel_arm_x, accel_arm_y, accel_arm_z, magnet_arm_x, magnet_arm_y, magnet_arm_z, roll_dumbbell, pitch_dumbbell, yaw_dumbbell, total_accel_dumbbell)

dataframevar <- sapply(dataframevar, as.numeric) #convert the variable to numeric
dataframeclasse<-select(data, classe) #select the classe variable
dataframe<-cbind(dataframeclasse,dataframevar) #bind the classe and other variables together
unique(dataframe$classe) #check the classe values
```` 

### Creating train and test datasets
We will split the dataset up into a training and a testset, so we can calculate a confidence matrix.

```{r}
inTrain <- createDataPartition(y=dataframe$classe, #we proberen class
                               p=0.7, list=FALSE)
training <- dataframe[inTrain,]
testing <- dataframe[-inTrain,]
dim(training); dim(testing)
```

### Random Forest model
From the selected variables we will create a Random Forest model based on the training set.
```{r}
modFit <- randomForest(classe~ .,data=training,method="rf") 
```


### Predicting the test dataset
Using the the created modFit model, we'll predict the classe in the testing dataaset.

```{r}
pred <- predict(modFit,testing)
testing$predRight <- pred==testing$classe #compare prediction with observed
```

From our confusion matrix we can see that the results have been predicted accurately.
```{r}
confusionMatrix(pred,testing$classe)
```


